A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories

### 2017-04-26 Camera-Ready/appendix.tex
uptodate

\appendix
%\section{Proofs of Theorems}
\section{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
\label{apx:thm2proof}
\begin{proof}
$\Gamma$ can be formalized using linear algebra:
Let $J$ be the adjacent matrix of $G_A$.
%Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
A vertex order on $G_A$ can be represented as 
%
%Since a vertex order is a permutation of $J$, the adjacent matrices 
%of any reordered graphs can be represented as 
$PJP^T$
where $P$ %$\in \mathbb{P}$ 
is a %$n\times n$ 
\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled}.
Consider an assignment matrix $B$ of star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$),
$B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix} holds.
% $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}, then $B$ is the assignment matrix of the star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
%
%In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is:
\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

@@

%The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t) = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
\end{split}
\end{equation*}
%Substitute back $t$ and $\mu$, we achieve the following concise form:
%\vspace{-1mm}
%\begin{equation*}
%\small
%\vspace{-1mm}
%	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
%\end{equation*}
This indicates the probability of $(\Gamma-d/2) \leq O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, Theorem 2 holds.
%it follows with probability greater than $(1-1/n)$, 
%$\Gamma - \Gamma^* \leq O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{d\log n}) $ following a similar reasoning.
\end{proof}

@@

\section{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\label{apx:spm_correct}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. 
%By the definition of star, $o_1$ $o_2$ belong to the same cluster at every timestamps in $P.T$. 
As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ be a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be outputted by Algorithm~\ref{algo:apriori_mining} from $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then by Lemma 3 %$\forall O' \subseteq O$,
the time sequence of %$O'$ 
any subset would not be eliminated by any $\mathtt{sim}$ operations.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. $level$ = 2 trivially holds. If $P.O \subset O_u$ at \emph{level $i$}, then any subsets of $P.O$ with size $i$ are in the candidate set. %In \emph{level} $i+1$, these subsets grow (in last iteration, they grow to $P.O$). 
This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. Since $P.O$ does not pruned by simplification, monotonicity and forward closure, $P$ must be returned by SPARE.
\end{proof}

>>>>

\appendix
%\section{Proofs of Theorems}
\section{Proofs of Theorem~\ref{THM:SPM_LB} and~\ref{THM:SPM_LB_INC}}
\label{apx:thm2proof}
\begin{proof}
$\Gamma$ can be formalized using linear algebra:
Let $J$ be the adjacent matrix of $G_A$.
%Let $G_A$ be an aggregated graph, with a $n \times n$ adjacent matrix $J$.
A vertex order on $G_A$ can be represented as 
%
%Since a vertex order is a permutation of $J$, the adjacent matrices 
%of any reordered graphs can be represented as 
$PJP^T$
where $P$ %$\in \mathbb{P}$ 
is a %$n\times n$ 
\emph{permutation matrix}~\footnote{An identity matrix with rows shuffled}.
Consider an assignment matrix $B$ of star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$),
$B=\triu(PJP^T)$~\footnote{$\mathtt{triu}$ is the upper triangle part of a matrix} holds.
% $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}, then $B$ is the assignment matrix of the star partitioning (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
%
%In star partitioning, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{Every element in $\vec{b}$ is $1$} 
vector with size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orderings, that is:
\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

@@

%The first step holds since all $b_{i,j}$ are 0-1 variables. 
Next, the event $(\max_{1 \leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, the following holds:
\begin{equation*}
\begin{split}
	Pr(\Gamma \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t) \\ &= Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) = n^{-1} = 1/n
\end{split}
\end{equation*}
%Substitute back $t$ and $\mu$, we achieve the following concise form:
%\vspace{-1mm}
%\begin{equation*}
%\small
%\vspace{-1mm}
%	Pr(\Gamma \geq (d/2 + \sqrt{n\log n})) \leq 1/n
%\end{equation*}
This indicates the probability of $(\Gamma-d/2) \leq O(\sqrt{n\log n})$ is $(1-1/n)$. 
Since $\Gamma^* \geq d/2$, Theorem 2 holds.
%it follows with probability greater than $(1-1/n)$, 
%$\Gamma - \Gamma^* \leq O(\sqrt{n\log n})$.
When the aggregated graph is \emph{dense} (i.e., $d\geq \sqrt{12 \log n}$),
the Chernoff Bound can be used to derive a tighter bound of 
$O(\sqrt{d\log n}) $ following a similar reasoning.
\end{proof}

@@

\section{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\label{apx:spm_correct}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. For any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. 
%By the definition of star, $o_1$ $o_2$ belong to the same cluster at every timestamps in $P.T$. 
As $P.T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ be a true pattern. Let $s$ be the object with the smallest ID in $P.O$. We prove that $P$ must be outputted by Algorithm~\ref{algo:apriori_mining} from $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then by Lemma 3 %$\forall O' \subseteq O$,
the time sequence of %$O'$ 
any subset would not be eliminated by any $\mathtt{sim}$ operations.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. $level$ = 2 trivially holds. If $P.O \subset O_u$ at \emph{level $i$}, then any subsets of $P.O$ with size $i$ are in the candidate set. %In \emph{level} $i+1$, these subsets grow (in last iteration, they grow to $P.O$). 
This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. Since $P.O$ does not pruned by simplification, monotonicity and forward closure, $P$ must be returned by SPARE.
\end{proof}

### 2017-04-26 Camera-Ready/sec1_introduction.tex
uptodate

\section{Introduction}
The prevalence of positioning devices has drastically boosted 
the scale and spectrum of trajectory collection to an unprecedented level. 
Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
records, are continually being generated from animal telemetry chips, 
vehicle GPSs and wearable devices. Data analysis on large-scale 
trajectories benefits a wide range of applications and services, 
including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, location-aware advertising~\cite{guo2016influence},  and social recommendations~\cite{bao2013survey}, to name just a few.

@@

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-movement patterns 
with different constraints with respect to clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}%~\cite{gudmundsson2006flock} 
and the \emph{convoy}%~\cite{jeung2008convoy} 
require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}%~\cite{li2010swarm}
does not impose any restriction. 
The \emph{group}%~\cite{wang2006grouppattern} 
and the \emph{platoon}%~\cite{li2015platoon} 
adopt a compromised approach by allowing
arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

\begin{table}[t]
\centering
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{1.7cm}|p{2.3cm}|}
\hline 
\textbf{Pattern} & {\textbf{Proximity}} & { \textbf{Conse-cutiveness}} & { \textbf{Time Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2006flock} & disk &  global & {$O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {$O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {$O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {$O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
%%\vspace{-0.5em}
\caption{Constraints and complexities of co-movement patterns. The time complexity indicates the performance wrt.
$|\mathbb{O}|$, $|\mathbb{T}|$ in the worst case, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
%\vspace{-0.5em}
\label{tbl:existing_co_patterns}
\end{table}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{ Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{ Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    %\vspace{-0.5em}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    %\vspace{-0.5em}
    \label{fig:related_work_scalability}
\end{figure}
%
%Therefore, in this paper, our contributions are closing
%these two gaps.
%
%to close these two gaps.
%
%Therefore, in this paper, our aim is to close these two gaps 
%via the following contributions.
%we aim to close these two gaps by making two contributions. 
In this paper, we resolve these two gaps by making the following contributions.
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP,
we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. It can be reduced to any of the previous pattern by customizing its parameters.

Second, we investigate deploying our GCMP detector on the model MapReduce platform (i.e., Apache Spark) to tackle the scalability issue. Our technical contributions are threefold. First, we design a baseline solution by replicating the snapshots 
%in multiple data chunks 
to support effective parallel mining. 
Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. 
SPARE achieves workload balance by partitioning objects into fine granular stars. 
For each partition, an Apriori Enumerator is adopted to mine the co-movement patterns. 
Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

>>>>

\section{Introduction}
The prevalence of positioning devices has drastically expanded 
the scale and spectrum of trajectory collection to an unprecedented level. 
Tremendous amounts of trajectories, in the form of sequenced spatial-temporal 
records, are continually being generated from animal telemetry chips, 
vehicle GPSs and wearable devices. Data analysis on large-scale 
trajectories benefits a wide range of applications and services, 
including traffic planning~\cite{zheng2011urban}, animal analysis~\cite{li2010miningperiodic}, location-aware advertising~\cite{guo2016influence},  and social recommendations~\cite{bao2013survey}, to name just a few.

@@

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-movement patterns 
with different constraints with respect to clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock} %~\cite{gudmundsson2006flock} 
and the \emph{convoy} %~\cite{jeung2008convoy} 
require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm} %~\cite{li2010swarm}
does not impose any restriction. 
The \emph{group} %~\cite{wang2006grouppattern} 
and the \emph{platoon} %~\cite{li2015platoon} 
adopt a compromised approach by allowing
arbitrary gaps between consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

\begin{table}[t]
\centering
\caption{Constraints and complexities of co-movement patterns. The complexity indicates the worst case performance, where $|\mathbb{O}|$ is the number of objects, and $|\mathbb{T}|$ is the number of discretized timestamps.}
\label{tbl:existing_co_patterns}
\begin{tabular}{|p{1.5cm}|p{1.4cm}|p{1.7cm}|p{2.2cm}|}
\hline 
{\small \textbf{Pattern}} & {\small \textbf{Proximity}} & {\small \textbf{Consecutive}} & {\small \textbf{Complexity}}\\ 
\hline 
flock~\cite{gudmundsson2006flock} & disk &  global & {\small $O(|\mathbb{O}||\mathbb{T}|\log(|\mathbb{O}|))$} \\ 
\hline 
convoy~\cite{jeung2008convoy} & density &   global & {\small $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
swarm~\cite{li2010swarm} & density  & - & {\small $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}  \\ 
\hline 
group~\cite{wang2006grouppattern} & disk &  local & {\small $O(|\mathbb{O}|^2|\mathbb{T}|)$}\\ 
\hline 
platoon~\cite{li2015platoon} & density &  local & {\small $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$}\\ 
\hline 
\end{tabular} 
\end{table}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{ Varying No. of objects} 
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{ Varying No. of timestamps}
    \label{fig:fig2}
    \end{subfigure}
    %\vspace{-0.5em}
    \caption{Performance measures on existing co-movement patterns. A sampled GeoLife dataset
    is used with upto 2.4 million data points. Default parameters are $M=15$, $K=180$, $L=30$.}
    %\vspace{-0.5em}
    \label{fig:related_work_scalability}
\end{figure}
%
%Therefore, in this paper, our contributions are closing
%these two gaps.
%
%to close these two gaps.
%
%Therefore, in this paper, our aim is to close these two gaps 
%via the following contributions.
%we aim to close these two gaps by making two contributions. 
In this paper, we close these two gaps by making the following contributions.
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP,
we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is also general. It can be reduced to any of the previous pattern by customizing its parameters.

Second, we investigate deploying our GCMP detector on the modern MapReduce platform (i.e., Apache Spark) to tackle the scalability issue. Our technical contributions are threefold. First, we design a baseline solution by replicating the snapshots 
%in multiple data chunks 
to support effective parallel mining. 
Second, we devise a novel \emph{Star Partitioning and ApRiori Enumerator} (SPARE) framework to resolve limitations of the baseline. 
SPARE achieves workload balance by partitioning objects into fine granular stars. 
For each partition, an Apriori Enumerator is adopted to mine the co-movement patterns. 
Third, we leverage the \emph{temporal monotonicity} property of GCMP 
to design several optimization techniques including \emph{sequence simplification}, \emph{monotonicity pruning} and \emph{forward closure check} to further reduce the number of candidates enumerated in SPARE.

### 2017-04-26 Camera-Ready/sec5_spm.tex
uptodate

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned TRPM scheme replicates snapshots based on the temporal dimension which suffers from two drawbacks. First, the replication factor $\eta$ can be large. Second, the same valid pattern may be redundantly discovered from different partitions.
%which results in redundant works.
To resolve these limitations,
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second stage of the map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMPs. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

Before we introduce the Apriori Enumerator, we are interested to 
examine the issue of global vertex ordering.
% on the moving objects.
This is because assigning different IDs to the objects will result in 
different star partitioning results, which will eventually affect the workload 
balance among reducers. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

@@

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
%\vspace{-0.5em}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$, i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.

>>>>

\section{SPARE: Star Partitioning and \\ Apriori Enumerator}
\label{sec:spm}
The aforementioned TRPM scheme replicates snapshots based on the temporal dimension which suffers from two drawbacks. First, the replication factor $\eta$ can be large. Second, the same valid pattern may be redundantly discovered from different partitions.
%which results in redundant works.
To resolve these limitations,
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second stage of the mapreduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMPs. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

@@

Before we introduce the Apriori Enumerator, we are interested to 
examine the issue of global vertex ordering.
% on the moving objects.
This is because assigning different IDs to the objects will produce 
different star partitioning results, which will eventually affect the workload 
balance among reducers. The job with the performance bottleneck is often known as a  \emph{straggler}~\cite{kwon2012skewtune}. In the context of star partitioning, a straggler refers to the job assigned with the maximum star partition. We use $\Gamma$ to denote the size of such straggler partition and $\Gamma$ is set to the number of edges in a directed star\footnote{A star is essentially a tree structure and the number of nodes equals the number of edges minus one.}. Clearly, a star partitioning with small $\Gamma$ is preferred. For example, Figure~\ref{fig:star-alt} gives two star partitioning results under 
different vertex ordering on the same graph. The top one has $\Gamma = 5$ while the bottom one has $\Gamma = 3$. Obviously, the bottom one with smaller $\Gamma$ is much more balanced.

@@

The maximal $G$-connected subsequence has the following two properties:
\begin{lemma}\label{lemma:union-property}
Suppose $\{T_1,T_2,\ldots,T_m\}$ is the set of all maximal $G$-connected subsequences of $T$, we have (1) $T_i\cap T_j=\emptyset$ for $i\neq j$ and (2) $T_1\cup T_2\cup\ldots\cup T_m=T$.
\end{lemma}
\begin{proof}
%\vspace{-0.5em}
We assume $T_i\cap T_j\neq \emptyset$. Let $T_i=(T_i[1], T_i[2],\ldots,T_i[p])$ and $T_j= (T_j[1], T_j[2],\ldots,T_j[n])$. Suppose $T[x]$ is a timestamp occurring in both $T_i$ and $T_j$. Let $T[y]=\min\{T_i[1],T_j[1]\}$ i.e., the minimum timestamp of $T_i[1]$ and $T_j[1]$ occurs at the $y$-th position of sequence $T$. Similarly, we assume $T[z]=\max\{T_i[p], T_j[n]\}$. Apparently, the two subsequences $T[y:x]$ and $T[x:z]$ are $G$-connected because $T_i$ and $T_j$ are both $G$-connected. Then, sequence $(T_y,\ldots,T_x,\ldots,T_z)$, the superset of $T_i$ and $T_j$, is also $G$-connected. This contradicts with the assumptions that $T_i$ and $T_j$ are maximal $G$-connected subsequences.
